---
title: "Analysis of audio norming"
output: html_document
---

# Set-up

Load packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("helpers.R")

theme_set(theme_bw())
```

Read in the data.
```{r}
dir <- "../data"
participant_files <- list.files(path = dir, full.names = TRUE)
audio_df <- plyr::ldply(participant_files, function(x) {
  read_csv(x)
})
audio_df <- audio_df %>% mutate_if(is.character, factor)
```

# Exclusions

Exclude test runs by the experimenter.
```{r}
audio_df <- audio_df %>% filter(!grepl("Elizabeth",comments))
```

Check the first languages of participants and exclude any non-English speakers.
```{r}
unique(audio_df$language)
audio_df <- audio_df %>% filter(grepl("english",language, 
                                      ignore.case = TRUE))
```

Examine the comments to see if anyone had difficulty with the task.
```{r}
unique(audio_df$comments)
```

# Demographics

Check the number of participants.
```{r}
length(unique(audio_df$participant_id))
```

Check the gender distribution.
```{r}
audio_df %>% group_by(gender) %>% 
  summarise(n = length(unique(participant_id)))
```

# Analysis

Create a column that says whether the participant selected action or object.
```{r}
audio_df <- audio_df %>% mutate(action_selected = case_when(
  selected_answer == "An action" ~ 1,
  selected_answer == "An object" ~ 0
))
```

Filter out the familiar words that we used at the beginning of the task.
```{r}
audio_fam <- audio_df %>% filter(word_type == "familiar")
```

Filter out the novel words that we are primarily interested in.
```{r}
audio_nov <- audio_df %>% filter(word_type == "novel")
```

## Familiar words

Find the proportion of people who said each word was an action.
```{r}
fam_sum <- audio_fam %>% group_by(word) %>% 
  summarise(action_prop = mean(action_selected))
```

In general, participants correctly identified whether the familiar words were an action or an objet.

## Novel words

Find the proportion of people who said each word was an action and construct confidence intervals.
```{r}
nov_sum <- audio_nov %>% group_by(word) %>% 
  summarise(action_prop = mean(action_selected),
            CI.low = ci.low(action_selected),
            CI.high = ci.high(action_selected)) %>%
  mutate(YMin = action_prop - CI.low, 
         YMax = action_prop + CI.high)
```

Graph these confidence intervals.
```{r}
ggplot(nov_sum, aes(x = word, y = action_prop, fill = word)) +
  geom_bar(stat = "identity") +
  ylab("proportion who selected word as action") +
  geom_errorbar(aes(ymin = action_prop-CI.low, 
                    ymax = action_prop+CI.high), width = .2) +
  ggtitle("Proportion of participants who judged word as action")
ggsave("../graphs/novel_word_judgments.pdf", width = 7, height = 5)
```

Examine the distance of the proportions from .5.
```{r}
nov_sum <- nov_sum %>% mutate(prop_dist = action_prop - .5)
```

