---
title: "Image norming analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set-up

Load packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("helpers.R")

theme_set(theme_bw())
```

Read in the data.
```{r}
dir <- "../data"
participant_files <- list.files(path = dir, full.names = TRUE)
img_df <- plyr::ldply(participant_files, function(x) {
  read_csv(x)
})
img_df <- img_df %>% mutate_if(is.character, factor)
```

# Exclusions

Exclude test runs by the experimenter.
```{r}
img_df <- img_df %>% filter(!grepl("Elizabeth",comments))
```

Check the first languages of participants and exclude any non-English speakers.
```{r}
unique(img_df$language)
img_df <- img_df %>% filter(grepl("english",language, 
                                      ignore.case = TRUE))
```

Examine the comments to see if anyone had difficulty with the task.
```{r}
unique(img_df$comments)
```

# Demographics

Check the number of participants.
```{r}
length(unique(img_df$participant_id))
```

Check the gender distribution.
```{r}
img_df %>% group_by(gender) %>% 
  summarise(n = length(unique(participant_id)))
```

# Analysis

Create a new dataframe that says for each image whether it was selected on a given trial.
```{r}
img_left <- img_df
img_right <- img_df

img_left <- img_left %>% 
  mutate(image = left_img, other_image = right_img)
img_right <- img_right %>% 
  mutate(image = right_img, other_image = left_img)

img_total <- rbind(img_left, img_right)
img_total <- img_total %>% 
  mutate(img_selected_true = ifelse(selected_img == image, 
                                    TRUE, FALSE))
```

Find the proportion of people who selected each image and construct confidence intervals.
```{r}
img_sum <- img_total %>% group_by(image, img_type) %>% 
  summarise(prop_selected = mean(img_selected_true), 
            CI.low = ci.low(img_selected_true),
            CI.high = ci.high(img_selected_true), n = n()) %>%
  mutate(YMin = prop_selected - CI.low, 
         YMax = prop_selected + CI.high)
```

## Novel images

Pull out novel actions and objects.
```{r}
img_sum_nov <- img_sum %>% filter(img_type == "novel")
img_sum_nov <- img_sum_nov %>% 
  mutate(img_kind = ifelse(grepl("action",image), "action", "object"))
```

Graph these confidence intervals for novel images.
```{r}
ggplot(img_sum_nov, aes(x = image, y = prop_selected, 
                        fill = img_kind)) +
  geom_bar(stat = "identity") +
  ylab("proportion who selected image") +
  geom_errorbar(aes(ymin = prop_selected-CI.low, 
                    ymax = prop_selected+CI.high), width = .2) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  scale_fill_manual(name = "image type", values = c("#eb4731", "#4e8df2")) +
  ggtitle("Proportion of participants who selected novel image: Version 2")
ggsave("../graphs/novel_imgs_v2.pdf", width = 8, height = 5)
```

## Familiar images

Pull out familiar actions and objects.
```{r}
img_sum_fam <- img_sum %>% filter(img_type == "familiar")
img_sum_fam <- img_sum_fam %>% 
  mutate(img_kind = ifelse(
    image == "ball" | image == "book" | image == "box" | 
      image == "dog" | image == "doll" | image == "hat" | 
      image == "horse" | image == "shoe",
    "object",
    "action"))
img_sum_fam$image <- factor(img_sum_fam$image, levels = c("cry", "draw", "drink", "eat", "read", "sit", "sleep", "wave", "ball", "book", "box", "dog", "doll", "hat", "horse", "shoe"))
```

Graph these confidence intervals for familiar images.
```{r}
ggplot(img_sum_fam, aes(x = image, y = prop_selected, 
                        fill = img_kind)) +
  geom_bar(stat = "identity") +
  ylab("proportion who selected image") +
  geom_errorbar(aes(ymin = prop_selected-CI.low, 
                    ymax = prop_selected+CI.high), width = .2) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  scale_fill_manual(name = "image type", values = c("#eb4731", "#4e8df2")) +
  ggtitle("Proportion of participants who selected familiar image: Version 2")
ggsave("../graphs/fam_imgs_v2.pdf", width = 8, height = 5)
```

## Individual participants

Add a column indicating whether participants selected the action as more interesting.
```{r}
img_df <- img_df %>% mutate(action_selected = 
                              ifelse(selected_word_type == "verb", 1, 0))
```

Calculate each participant's proportion of trials on which they selected the action.
```{r}
img_sum_partic <- img_df %>% group_by(participant_id, img_type) %>%
  summarise(action_prop = mean(action_selected),
            CI.low = ci.low(action_selected),
            CI.high = ci.high(action_selected)) %>%
  mutate(YMin = action_prop - CI.low, 
         YMax = action_prop + CI.high)
```

Plot participants' proportion of trials on which they selected the action as more interesting.
```{r}
ggplot(img_sum_partic, aes(x = as.factor(participant_id), y = action_prop,
                           fill = img_type)) +
  geom_bar(stat = "identity") +
  xlab("participant") +
  ylab("proportion of trials participant selected action") +
  scale_fill_manual(name = "image type", values = c("#eb4731", "#4e8df2")) +
  facet_wrap(. ~ img_type) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  ggtitle("Participants' proportion of words judged as actions: Version 2")
ggsave("../graphs/participant_prop_action_v2.pdf", width = 10, height = 5)
```

## Overall proportion of selecting action image

Calculate the overall proportion of trials on which the action was selected, for familiar and novel words.
```{r}
img_avg <- img_df %>% group_by(img_type) %>% 
  summarise(m = mean(action_selected),
            CI.low = ci.low(action_selected),
            CI.high = ci.high(action_selected)) %>%
  mutate(YMin = m - CI.low, 
         YMax = m + CI.high)
```

Graph the overall proportions.
```{r}
ggplot(img_avg, aes(x = img_type, y = m, 
                        fill = img_type)) +
  geom_bar(stat = "identity") +
  xlab("trial type") +
  ylab("proportion who selected action image") +
  geom_errorbar(aes(ymin = m-CI.low, 
                    ymax = m+CI.high), width = .2) +
  scale_fill_manual(name = "trial type", values = c("#eb4731", "#4e8df2")) +
  ggtitle("Proportion of trials with action image selected: Version 2")
ggsave("../graphs/overall_prop_action_v2.pdf", width = 5, height = 5)
```

